% Jerry_Smith_resume.tex

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
%\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\resheading}[1]{{\large{\colorbox{MyGrey}{\textbf{\fontfamily{phv}\selectfont #1 \vphantom{p\^{E}}}}}}}
%\newcommand{\resheading}[1]{{\large{\textbf{\fontfamily{phv}\selectfont #1 \vphantom{p\^{E}}}}}}
%\newcommand{\resheading}[1]{{\large{\textbf{\textcolor{MyNameColor}{\fontfamily{phv}\selectfont #1 \vphantom{p\^{E}}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

\usepackage{mathpazo}
\usepackage[usenames,dvipsnames]{color}
\definecolor{MyNameColor}{rgb}{0.18,0.31,0.31}
\definecolor{MyGrey}{rgb}{0.85,0.85,0.85}
\usepackage{url}

\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Huge\textcolor{MyNameColor}{{\fontfamily{phv}\selectfont Jerry D. Smith II}}}  & 505-565-2628 (home)\\
23 Valencia Rd.                                      & 505-284-9782 (office) \\
Peralta, NM                                     & 505-500-4868 (mobile) \\
                                                          & \texttt{jerry.d.smith.ii@gmail.com} \\
\end{tabular*}
\\

\vspace{0.1in}

%
% TODO: Objective
%
\resheading{Objective}

\vspace{0.1in}
I would like to use my knowledge of Linux, HP-UX, OSX, Solaris, OS deployment, networks,
network security, the web, high performance computing, clusters, massively
scalable systems, high performance parallel filesystems, system administration, distributed resource management,
relational databases, and configuration management, to create
world-class systems and applications.
\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
    \ressubheading{Los Lunas High School}{Los Lunas, NM}{Secondary studies}{Graduation 1994}

\end{itemize}

\vspace{0.1in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% START: WORK EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
\begin{itemize}
\item
    \ressubheading{Sandia National Laboratories}{Albuquerque, NM}{Enterprise Linux Architect for Oracle Systems }{November 2010 -- present}
    \begin{itemize}
        \resitem{Conduct day-to-day monitoring, operation, troubleshooting, user support, etc. on Oracle Enterprise Platforms.}
        \resitem{Designed and implemented 42 node D/Q/P/DR solution for E-business Suite on Oracle Enterprise Linux.}
        \resitem{Designed and implemented repeatable build platform utilizing kickstart and pxe for Enterprise Linux environment .}
         \resitem{Designed and implemented configuration management  solution with Git and Puppet .}
        \resitem{Designed and Implemented pro-active monitoring, reporting, system base lining  using Ganglia and Nagios.}
        \resitem{Designed and implemented a large suite of tools used to manage the Oracle Enterprise Platforms.}
    \end{itemize}
\item
    \ressubheading{Sandia National Laboratories .}{Albuquerque, NM}{Systems Administrator}{Jan 2003 -- Nov 2010}
    \begin{itemize}
        \resitem{Architecture, development, and implementation of Linux solutions with emphasis on clusters for high performance and scientific computing.}
        \resitem{Member of the Thunderbird implementation team: \#5 on the top500 list - 8,960 compute node CPUs on SDR InfiniBand.}

        \resitem{Member of engineering team who designed and implemented the Red Sky supercomputer: \#10 on the November 2009 top500 list with 433.5 TFlop/s. 43,008 cores on a 3D torus using QDR InfiniBand.}
        \resitem{Presented OSX server cluster for Sandia National Laboratories in the ASCI booth at SC2004.}
        \resitem{Deployed Apache web platform for the Infrastructure Computing Systems Department.}
        \resitem{Created health-monitoring scripts that page system administrators when Linux cluster problems are detected.}
        \resitem{Development and presentation of training materials for user and administrator communities}
       \end{itemize}

\item
    \ressubheading{Sandia National Laboratories}{Albuquerque, NM}{Distributed Resource Management Analyst}{Jan 2003 -- Nov 2010}
    \begin{itemize}
       \resitem{Sandia Technical Lead for Tri-Lab "HPC Common Resource Management".}
       \resitem{Contributor to RFI/RFP/Selection of Common Resource Management Solution}
       \resitem{Deployment, development, and administration of Moab Scheduler}
       \resitem{Deployment, development, and administration of Torque Resource Manager.}
       \resitem{Deployment, development, and administration of Slurm Resource Manager.}
       \resitem{Lead development of in house cluster accounting, utilization, and reporting along with accompanying web services to provide these metrics.}
    \end{itemize}



\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% END: WORK EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}
\begin{description}
\item[Languages and Programming:]  Perl, PHP, Ruby,  \LaTeX, Shell, SQL,  HTML, git, CVS, SVN, Eclipse, Netbeans.
\item[Operating Systems:] Linux (Ubuntu, RedHat, Gentoo, Oracle Enterprise Linux), Solaris, OSX
\item[Clustering/HPC:] PBS/Torque, Maui, Slurm, Moab, Myrinet, InfiniBand
\item[Database:] MySQL, Oracle, PostgreSQL, SQLite
\item[Web:] Apache, Apache C/Perl API, HTML::Mason, mod\_perl, CGI, DBI, PHP, Ruby on Rails, Tomcat, JBoss.
\item[Miscellaneous:] Excellent troubleshooting and debugging skills, self-motivated, customer focused, and highly organized.
\end{description}

\resheading{Publications}
\begin{itemize}
    \item Jerry D. Smith II.  Tuning For Massive Systems; {\sl Moab-Con}.  May 28-30 , 2008, Provo, UT.
    \item Jerry D. Smith II.  Thunderbird Capacity Computing System; {\sl LCI Conference on High Performance Computing} May 3, 2006,  Norman, OK.
\end{itemize}

\resheading{Other}
\begin{itemize}
    \item Active DOE ``Q''-level security clearance.
    \item Red Hat Certified Engineer RHEL 5; cert \#805008184632534, June 27, 2008
    \item Red Hat Certified Systems Administrator RHEL 6;  cert \#110-272-069,  July 15, 2011 
\end{itemize}

%\resheading{References}
%\begin{itemize}
  %   \item Available Upon Request
 %\end{itemize}

\end{document}
